---
title: "Frequently Asked Questions"
author: "Brandon Bertelsen"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## FAQ

### How do I hide the question numbers?

A number of theme options exist for this purpose, `format_var_alias`, `format_var_description`, `format_var_filtertext`, and `format_var_name`. In your format list, set an item `include_q_number = FALSE` as in the example below.

```{r, eval = FALSE}
myAwesomeTheme = themeNew(
  ..., # your other theme options
  format_var_description = list(include_q_number = FALSE),
  format_var_filtertext = list(include_q_number = FALSE)
)
```

### How do I make it so that there is more than one question per page?

```{r, eval = FALSE}
myAwesomeTheme = themeNew(
  ...,
  one_per_sheet = FALSE
)
```

### How do I output numbers like 1,000 instead of 1000?

```{r, eval = FALSE}
format(1000, nsmall=0, big.mark=",")
```

### How do I add a subtitle to my document?

A common usage of the subtitle is to include the survey's field window. Especially for studies that are run continuously.

```{r, eval = FALSE}
writeLatex(
  ...,
  subtitle = "My Amazing Subtitle"
)
```

### How do I append more information?

See the section about appending text in the [overview](articles/overview.html#appending-text-pdf-only)

### How do I mask questions with low base sizes?

Below is an example of masking responses where the base size is less than the central limit theorem with a "-" character.

```{r, eval = FALSE} 
myAwesomeTheme = themeNew(
  ...,
  format_min_base = list(mask = "-", min_base = 30)
)
```

### How do I install a different release of crunchtabs?

In the code example below we show you how to install Release 1.2.1:

```{r, eval = FALSE}
remotes::install_github("Crunch-io/crunchtabs@v1.2.1")
```

### How do I replace question numbers with question aliases?

We can manipulate the crosstab object so that instead of displaying a number, we display the question alias. 
```{r, eval = FALSE}
ds = loadDataset("Example dataset")
# Use ds = newExampleDataset() if it doesn't work
ct = crosstabs(ds)

nms = names(ct$results)
for(i in 1:results) {
  ct$results[[i]]$number = i
}

writeLatex(ct, ...)
```

Instead of: 

> 1. This is my question text

You should see: 

> question_alias. This is my question text

### How do I request a new feature? 

We welcome features requests as new issues to the [crunchtabs github repository](https://github.com/Crunch-io/crunchtabs/issues)
