---
title: "Frequently Asked Questions"
author: "Brandon Bertelsen"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## FAQ

### How do I hide the question numbers?

A number of theme options exist for this purpose, `format_var_alias`, `format_var_description`, `format_var_filtertext`, and `format_var_name`. In your format list, set an item `include_q_number = FALSE` as in the example below.

```{r, eval = FALSE}
myAwesomeTheme = themeNew(
  ..., # your other theme options
  format_var_description = list(include_q_number = FALSE),
  format_var_filtertext = list(include_q_number = FALSE)
)
```

### How do I make it so that there is more than one question per page?

```{r, eval = FALSE}
myAwesomeTheme = themeNew(
  ...,
  one_per_sheet = FALSE
)
```

### How do I output numbers like 1,000 instead of 1000?

```{r, eval = FALSE}
format(1000, nsmall=0, big.mark=",")
```

### How do I add a subtitle to my document?

A common usage of the subtitle is to include the survey's field window. Especially for studies that are run continuously.

```{r, eval = FALSE}
writeLatex(
  ...,
  subtitle = "My Amazing Subtitle"
)
```

### How do I append more information?

See the section about appending text in the [overview](articles/overview.html#appending-text-pdf-only)

### How do I mask questions with low base sizes?

Below is an example of masking responses where the base size is less than the central limit theorem with a "-" character.

```{r, eval = FALSE} 
myAwesomeTheme = themeNew(
  ...,
  format_min_base = list(mask = "-", min_base = 30)
)
```

### How do I display questions with different weights in the same report?

We can chain crosstabs objects easily to create the desired effect: 

```{r, eval = FALSE}
# ...
topline_summary = crosstabs(ds, vars = c("a", "b"), weight = "weightvar")
chain_me = crosstabs(ds, vars = c("c"), weight = "other_weightvar")

topline_summary$results = c(
  topline_summary$results, 
  chain_me$results
)

topline_summary$results = crunchtabs:::reflowQuestionNumbers(
  topline_summary$results
)

writeLatex(topline_summary)
```

Re-weighting the same variable with another weight in the same report is possible but requires you to also adjust the names so that you can edit the question text appropriately to demonstrate the different weighting: 

```{r, eval = FALSE}
# ...
topline_summary = crosstabs(ds, vars = c("a", "b"), weight = "weightvar")
chain_me = crosstabs(ds, vars = c("a"), weight = "other_weightvar")

names(chain_me$results) = "a_other_weight_var" # rename the alias
chain_me$results$a_other_weight_var$description = "This is question text (weighted by other_weight_var)"

topline_summary$results = c(
  topline_summary$results, 
  chain_me$results
)

topline_summary$results = crunchtabs:::reflowQuestionNumbers(
  topline_summary$results
)

writeLatex(topline_summary)
```


### How do I install a different release of crunchtabs?

In the code example below we show you how to install Release 1.2.1:

```{r, eval = FALSE}
remotes::install_github("Crunch-io/crunchtabs@v1.2.1")
```

### How do I request a new feature? 

We welcome features requests as new issues to the [crunchtabs github repository](https://github.com/Crunch-io/crunchtabs/issues)
