---
title: "Frequently Asked Questions"
author: "Brandon Bertelsen"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## FAQ

### How do I change the crosstab stub width?

The stub width (the first column of a crosstabulation) is fixed at 1.5inches by default. In v1.2.3 we added a feature allowing an override. 

```{r, eval = FALSE}
myTheme = themeNew(
  ... # your other theme optinos
  format_label_column = list(col_width = 2)
)
```

The code example above would set the stub width to 2 inches. For a PDF document, col_width is in inches. You can also create an exceptional stub width for one or more questions, as follows:

```{r, eval = FALSE}
myTheme = themeNew(
  ... # your other theme optinos
  format_label_column_exception = c("alias"=2.5, "otheralias"=1.25)
)
```

In this case, you create a named numeric vector where the name is the question alias whose stub width you wish to change and the numeric value is the stub width in inches. 

### How do I hide the question numbers?

A number of theme options exist for this purpose, `format_var_alias`, `format_var_description`, `format_var_filtertext`, and `format_var_name`. In your format list, set an item `include_q_number = FALSE` as in the example below.

```{r, eval = FALSE}
myAwesomeTheme = themeNew(
  ..., # your other theme options
  format_var_description = list(include_q_number = FALSE),
  format_var_filtertext = list(include_q_number = FALSE)
)
```

### How do I make it so that there is more than one question per page?

```{r, eval = FALSE}
myAwesomeTheme = themeNew(
  ...,
  one_per_sheet = FALSE
)
```

### How do I output numbers like 1,000 instead of 1000?

```{r, eval = FALSE}
format(1000, nsmall=0, big.mark=",")
```

### How do I add a subtitle to my document?

A common usage of the subtitle is to include the survey's field window. Especially for studies that are run continuously.

```{r, eval = FALSE}
writeLatex(
  ...,
  subtitle = "My Amazing Subtitle"
)
```

### How do I append more information?

See the section about appending text in the [overview](articles/overview.html#appending-text-pdf-only)

### How do I mask questions with low base sizes?

Below is an example of masking responses where the base size is less than the central limit theorem with a "-" character.

```{r, eval = FALSE} 
myAwesomeTheme = themeNew(
  ...,
  format_min_base = list(mask = "-", min_base = 30)
)
```

### How do I install a different release of crunchtabs?

In the code example below we show you how to install Release 1.2.1:

```{r, eval = FALSE}
remotes::install_github("Crunch-io/crunchtabs@v1.2.1")
```

### How do I request a new feature? 

We welcome features requests as new issues to the [crunchtabs github repository](https://github.com/Crunch-io/crunchtabs/issues)
